\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-07 forwards-and-backwards.tex
Update on Overleaf.

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}[theorem]{Example}
\newtheorem{definition}[theorem]{Definition}

\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
\def \non{{\nonumber}}
\def \hat{\widehat}
\def \tilde{\widetilde}
\def \bar{\overline}
\newcommand{\IP}{\mathbb P}
\newcommand{\IQ}{\mathbb Q}
\newcommand{\IE}{\mathbb E}
\newcommand{\IR}{\mathbb R}
\newcommand{\IZ}{\mathbb Z}
\newcommand{\IN}{\mathbb N}
\newcommand{\IT}{\mathbb T}
\newcommand{\IC}{\mathbb C}
\newcommand{\ind}{\mathbf{1}}
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\grad}{\nabla}

@@

\begin{definition}[Martingale Problem Characterisation]
    \label{Def: Rescaled Models}
We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^{\theta}_0$,
such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
\begin{equation}
    \label{eq: Pre-limit Martingale Characterisation}
\begin{aligned}
&     M^{\theta}_t(f)\\
:=&  \langle f,\eta^{\theta}_t \rangle
        -\langle f,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        f(z)r\big(z,\varrho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\varrho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int 
f(x)F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
\begin{equation}
\begin{aligned}
[ M^{\theta}_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\varrho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
\end{aligned}    
\end{equation}

@@

% % % % % % % % % % % % % % % %
\subsection*{Lookdown Representation and Notation}
\label{sec: Lookdown Representation and Notation}

@@

Explicitly, in the $\theta$-th stage of re-scaling,
an individual has mass $\frac{1}{\lambda} := \frac{1}{N}$
and a level between $[0,N]$;
the established birth rate $\gamma(x,\eta)$ is
$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)
:=~\theta\gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy);$$
the local branching mechanism $b(x,\eta)$ is 
$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
and the dispersal kernel $q^{\mathfrak{m}}(x,dy)$ is 
$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) 
:=~ \frac{r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$

@@

\begin{remark}
In Appendix \ref{sec: Markov Mapping Theorem Application},
applying Markov Mapping Theorem,
we will show that the spatial projection of $(\xi^{\theta}_t)_{t \geq 0}$ defined as 
$$(\eta^{\theta}(t))_{t \geq 0}
:=\left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \xi^{\theta}(t)} \delta_{X(t)}\right)_{t \geq 0}$$
has the same distribution (as stochastic processes)
as $(\eta^{\theta}_t)_{t \geq 0}$
in Definition \ref{Def: Rescaled Models}.
As a result, we use the same notation $\eta$
to denote these two identically distributed processes
which take values in the space of empirical measures.
On the other hand,
we reserve the notation $\xi$
strictly for the spatial-level process.

@@

Theorem A.10 in \cite{kurtz/rodrigues:2011}
states that convergence of $(\eta^{\theta}_t)_{t \geq 0}$
to a conditionally Poisson system $(\xi_t)_{t \geq 0}$
with Cox measure $\Xi_t \times N$
is equivalent to convergence of
$(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
As a result, it suffices for us to focus on
tightness of $(\eta^{\theta}_t)_{t \geq 0}$
and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$
as $\theta \to \infty$.

@@

Here we give a general framework of tracking evolution of individual particles in the population described above. We will provide the right scaling of the coefficients introduced in \S \ref{sec: Convergence of Spatial-Level Models}.\\
Particles alive at time zero will be indexed by
$(0, i)$, or more precisely, we index the levels of the particles alive at time $0$ by $(0, i)$ keeping
in mind that at each birth event, the parent particle will, with probability $1/2$ change levels.
Since no two particles born after time $0$ will be born at the same time, we index the rest of
the levels by their birth times. With each level, we can associate a Poisson random measure
$\xi$ on $[0, \infty)^2\times [0,1]\times \{0,1\}$ (eventually, $\lambda \to \infty$) with mean measure $l^3 \times \{\frac{1}{2}\delta_0,\frac{1}{2}\delta_1\}$ which
determines the birth times of the offspring of the particle at that level, the location of the
offspring, and whether the offspring or the parent is placed at the new level. Let $U_{\tau}(t)$ be
the level at time $t \geq \tau$ if the level first appeared at time $\tau$ , and let $X_{\tau}(t), t \geq \tau$ be the
location of the particle with level $U_{\tau}(t)$. 
Now $U_{\tau}$ satisfies
U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s),\eta(s))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds, ~~~ t \geq \tau.    
If a level has index $\tau$ and $(s,v,w,\kappa)\in \xi_\tau$, then $\tau+s$ gives a potential birth time for an offspring of the particle at level $U_{\tau}$. We say `potential' since if $U_{\tau}(\tau+s)>\lambda$, the corresponding particle is dead. The (potential) new level is 
\begin{equation}\label{New birth potential level}
    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
If $U_{\tau+s}(\tau+s)< \lambda$, a new particle is produced with location $X_{\tau}(\tau+s-)+H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ where $H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ is a function such that if $w$ is a uniformly distribution on $[0,1]$, then 
\begin{equation}\label{eq: Individual Evolution Jump Kernel}
P(H(x, \eta,w)\in C | \eta,x)=q^{\mathfrak{m}}(x, \eta,C).    
Consequently, 
$$X_{\tau}(\tau+s)=X_{\tau}(\tau+s-)+\kappa H(X_{\tau}(\tau+s-), \eta(\tau+s),w)$$
and 
$$X_{\tau+s}(\tau+s)=X_{\tau}(\tau+s-)+(1-\kappa) H(X_{\tau}(\tau+s-), \eta(\tau+s),w),$$
that is if $\kappa=0$, the parent stays at its current level and the new particle is given the new
level. If $\kappa = 1 $, the parent is given the new level and the new particle is given the original
level. Consequently, for $t \geq \tau$
\begin{align}\label{eq: Spatial evolution of individual lineage}
X_{\tau}(\tau+t)=&X_{\tau}(t)\\
&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
&\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
Starting with an initial particle at level $U_{(0,i)}$ , we can identify a potential line of descent by
taking $(s_1 , v_1 , w_1 , \kappa_1 ) \in \xi_{(0,i)}$ , setting $\tau_1=s_1$ , and then recursively taking $(s_k , v_k , w_k , \kappa_k ) \in \xi_{\tau_k }$ and defining $\tau_{k+1} = \tau_{k} + s_{k+1}$. Each time $\tau$ at which a new level appears has an “ancestory” of this type.\\
We now explain the cases where $\kappa_k=0$ and $\kappa_k=1$. When $\kappa_k=0$, the parent retains the level, so $X_{\tau_{k}}$ remains the same at time $\tau_{k+1}$. When $\kappa_k=1$, the offspring gets its parent's level while the parent inherits a new level sampled between $[U_{\tau_k}(\tau_{k+1}-),\lambda]$. As a result, the spatial location $X_{\tau_{k}}$ jumps from the parent's location to the offspring's location at time $\tau_{k+1}$.  Meanwhile, between $[\tau_k, \tau_{k+1}]$ there maybe further birth events generated by $\xi_{\tau_k}$. If $(s,v,w,\kappa) \in \xi_{\tau_k}$, Equation \eqref{eq: Spatial evolution of individual lineage} holds and gives the spatial evolution of $X_{\tau_k}$ for $t \in [\tau_k, \tau_{k+1}]$.\\

@@

    \begin{equation}\label{eq: gamma - r radius comparison bound}
    \gamma\big(x,\varrho_{\gamma}*\eta(x)\big) \left| \theta \int_{\mathbb{R}^n} \big\{f\big(\varrho_{r}*\eta(y)\big)-f\big(\varrho_{r}*\eta(x)\big)\big\}\varrho_{1/\theta}(x-y)dy\right| \leq C_{\gamma, f}    
    \end{equation}
    for some constant $C_{\gamma,f}$ independent of $\eta$ and $\theta$. 
\end{lemma}
\begin{proof}
See Appendix.    
\end{proof}
\begin{lemma}[Compact Containment for the population process]
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
    uniformly in $\theta$.
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that

@@

>>>>

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}[theorem]{Example}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{notation}[theorem]{Notation}

\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
\def \non{{\nonumber}}
\def \hat{\widehat}
\def \tilde{\widetilde}
\def \bar{\overline}
\newcommand{\IP}{\mathbb P}
\newcommand{\IQ}{\mathbb Q}
\newcommand{\IE}{\mathbb E}
\newcommand{\IR}{\mathbb R}
\newcommand{\IZ}{\mathbb Z}
\newcommand{\IN}{\mathbb N}
\newcommand{\IT}{\mathbb T}
\newcommand{\IC}{\mathbb C}
\newcommand{\ind}{\mathbf{1}}
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\grad}{\nabla}
\newcommand{\dif}{\mathrm{d}\,}

@@

\begin{definition}[Martingale Problem Characterisation]
    \label{Def: Rescaled Models}
We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^{\theta}_0$,
such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
\begin{equation}
    \label{eq: Pre-limit Martingale Characterisation}
\begin{aligned}
M^{\theta}_t(f)
&:=  \langle f,\eta^{\theta}_t \rangle
        -\langle f,\eta^{\theta}_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\varrho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\varrho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad {} +\int 
     f(x)F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
\begin{equation}
\begin{aligned} \relax
[ M^{\theta}_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\varrho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
\end{aligned}    
\end{equation}

@@

% % % % % % % % % % % % % % % %
\subsection{Lookdown Representation and Notation}
\label{sec: Lookdown Representation and Notation}

@@

Explicitly, in the $\theta$-th stage of re-scaling,
an individual has mass $\frac{1}{\lambda} := \frac{1}{N}$
and a level between $[0,N]$;
the established birth rate $\gamma(x,\eta)$ is
$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)
:=~\theta\gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy);$$
the local branching mechanism $b(x,\eta)$ is 
$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
and the dispersal kernel $q^{\mathfrak{m}}(x,\eta, dy)$ is 
$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) 
:=~ \frac{r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$

@@

\begin{remark}
In Appendix \ref{sec: Markov Mapping Theorem Application},
applying Markov Mapping Theorem,
we will show that the spatial projection of $(\xi^{\theta}_t)_{t \geq 0}$ defined as 
$$(\eta^{\theta}(t))_{t \geq 0}
:=\left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \xi^{\theta}(t)} \delta_{X(t)}\right)_{t \geq 0}$$
has the same distribution (as stochastic processes)
as $(\eta^{\theta}_t)_{t \geq 0}$
in Definition \ref{Def: Rescaled Models}.
As a result, we use the same notation $\eta$
to denote these two identically distributed processes.
On the other hand,
we reserve the notation $\xi$
strictly for the spatial-level process.

@@

Theorem A.10 in \cite{kurtz/rodrigues:2011}
states that convergence of $(\eta^{\theta}_t)_{t \geq 0}$
to a conditionally Poisson system $(\xi_t)_{t \geq 0}$
with Cox measure $\Xi_t \times N$
is equivalent to convergence of
$(\eta^{\theta}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
As a result, it suffices for us to focus on
tightness of $(\eta^{\theta}_t)_{t \geq 0}$
and spatial convergence of $(\eta^{\theta}_t)_{t \geq 0}$
as $\theta \to \infty$.

@@

Here we give a general framework of tracking evolution
of individual particles in the spatial-level population $\xi(t)_{t \geq 0}$ defined in \S \ref{sec: Lookdown Representation and Notation}.

Particles alive at time zero will be indexed by $(0, i)$,
or more precisely,
we index the levels of the particles
alive at time $0$ by $(0, i)$,
keeping in mind that at each birth event,
the parent particle will,
with probability $1/2$, change levels.
Since no two particles born after time $0$
will be born at the same time,
we index the rest of the levels by their birth times.

With each level,
we can associate a Poisson random measure
$\Tilde{\Pi}$ on $[0, \infty)^2\times [0,1]\times \{0,1\}$ (eventually, $\lambda \to \infty$) with mean measure $l^3 \times \{\frac{1}{2}\delta_0,\frac{1}{2}\delta_1\}$ which
determines the birth times of the offspring of the particle at that level, the location of the
offspring, and whether the offspring or the parent is placed at the new level. Let $U_{\tau}(t)$ be
the level at time $t \geq \tau$ if the level first appeared at time $\tau$ , and let $X_{\tau}(t), t \geq \tau$ be the
location of the particle with level $U_{\tau}(t)$. 
Now $U_{\tau}$ satisfies
\begin{equation}
U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s),\eta(s))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds, ~~~ t \geq \tau.    
\end{equation}
If a level has index $\tau$ and $(s,v,w,\kappa)\in \xi_\tau$, then $\tau+s$ gives a potential birth time for an offspring of the particle at level $U_{\tau}$. We say `potential' since if $U_{\tau}(\tau+s)>\lambda$, the corresponding particle is dead. The (potential) new level is 
\begin{equation}\label{New birth potential level}
    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
\end{equation}
If $U_{\tau+s}(\tau+s)< \lambda$, a new particle is produced with location $X_{\tau}(\tau+s-)+H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ where $H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ is a function such that if $w$ is a uniformly distribution on $[0,1]$, then 
\begin{equation}\label{eq: Individual Evolution Jump Kernel}
P(H(x, \eta,w)\in C | \eta,x)=q^{\mathfrak{m}}(x, \eta,C).    
\end{equation}
Consequently, 
$$X_{\tau}(\tau+s)=X_{\tau}(\tau+s-)+\kappa H(X_{\tau}(\tau+s-), \eta(\tau+s),w)$$
and 
$$X_{\tau+s}(\tau+s)=X_{\tau}(\tau+s-)+(1-\kappa) H(X_{\tau}(\tau+s-), \eta(\tau+s),w),$$
that is if $\kappa=0$, the parent stays at its current level and the new particle is given the new
level. If $\kappa = 1 $, the parent is given the new level and the new particle is given the original
level. Consequently, for $t \geq \tau$
\begin{align}\label{eq: Spatial evolution of individual lineage}
X_{\tau}(\tau+t)=&X_{\tau}(t)\\
&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
&\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
\end{align}
Starting with an initial particle at level $U_{(0,i)}$ , we can identify a potential line of descent by
taking $(s_1 , v_1 , w_1 , \kappa_1 ) \in \xi_{(0,i)}$ , setting $\tau_1=s_1$ , and then recursively taking $(s_k , v_k , w_k , \kappa_k ) \in \xi_{\tau_k }$ and defining $\tau_{k+1} = \tau_{k} + s_{k+1}$. Each time $\tau$ at which a new level appears has an “ancestory” of this type.\\
We now explain the cases where $\kappa_k=0$ and $\kappa_k=1$. When $\kappa_k=0$, the parent retains the level, so $X_{\tau_{k}}$ remains the same at time $\tau_{k+1}$. When $\kappa_k=1$, the offspring gets its parent's level while the parent inherits a new level sampled between $[U_{\tau_k}(\tau_{k+1}-),\lambda]$. As a result, the spatial location $X_{\tau_{k}}$ jumps from the parent's location to the offspring's location at time $\tau_{k+1}$.  Meanwhile, between $[\tau_k, \tau_{k+1}]$ there maybe further birth events generated by $\xi_{\tau_k}$. If $(s,v,w,\kappa) \in \xi_{\tau_k}$, Equation \eqref{eq: Spatial evolution of individual lineage} holds and gives the spatial evolution of $X_{\tau_k}$ for $t \in [\tau_k, \tau_{k+1}]$.\\

@@

    \begin{equation}\label{eq: gamma - r radius comparison bound}
    \gamma\big(x,\varrho_{\gamma}*\eta(x)\big) \left| \theta \int_{\mathbb{R}^n} \big\{f\big(\varrho_{r}*\eta(y)\big)-f\big(\varrho_{r}*\eta(x)\big)\big\}\varrho_{1/\theta}(x-y)dy\right| \leq C_{\gamma, f}    
    \end{equation}
    for some constant $C_{\gamma,f}$ independent of $\eta$ and $\theta$. 
\end{lemma}
\begin{proof}
See Appendix \ref{sec: Proof to gamma-r radius comparison}.    
\end{proof}
\begin{lemma}[Compact Containment for the population process]
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
    uniformly in $\theta$.
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that

@@

\subsubsection{Porous Media Equation}

\plr{This is from pme.tex.}

We are concerned with non-negative solutions to the equation
\begin{equation}
\label{mollified equation}
\frac{\partial u^\epsilon}{\partial t}=
%\frac{\partial^2}{\partial x^2}
\Delta\left(u^\epsilon \cdot u^\epsilon *\zeta_\epsilon\right)
+u^\epsilon\left(1-u^\epsilon*\zeta_\epsilon\right);
\end{equation}
where $*$ denotes convolution and we define
a (non-negative) mollifier by
$\zeta_\epsilon=\frac{1}{\epsilon}\zeta(\cdot/\epsilon)$, where $\zeta$
satisfies
$\zeta\in\cal{S}(\IR)$, $\int\zeta(x)dx=1$. Indeed, for convenience, in
what follows we shall suppose that $\zeta =\rho*\check{\rho}$ where
$\check{\rho}(z)=\rho(-z)$ and $\rho$ has
compact support, although that
is certainly stronger than we need.
In particular, we should like to prove that as $\epsilon\to 0$ we have
convergence to the solution to the porous medium equation with
logistic growth:
\begin{equation}
\label{PME}
\frac{\partial u}{\partial t}=
%\frac{\partial^2}{\partial x^2}
\Delta\left(u^2\right)
+u\left(1-u\right).
\end{equation}

We work on $[0,T]\times \IT_K$ where $\IT_K$ is the one-dimensional
torus of size $K$, and $T,K>0$ are fixed but arbitrary.

\begin{remark}
By taking a sequence $K_n\to\infty$, and doing a bit of work,
we can presumably then recover the result
we need for, e.g., a population expanding its range from a compact
set containing the origin (for which we know the solution to the PME
converges to two travelling waves, travelling in opposite directions
\cite{kamin/rosenau:2004}). Such waves have bounded support, even when
we consider the equation on
the whole real line, and travel at a fixed speed, so don't feel the boundedness
of the torus,
so this should be straightforward. The challenge will be to control the
mass of the approximating functions that falls beyond that wavefront,
since they themselves will have full support and so arguably `feel' that they
are on the torus.
It is not clear that it is worth doing the details for this paper - this is
meant as an example.
\end{remark}

\begin{notation}

Whenever we integrate with respect to $x$, this is implicitly over the
whole torus $\IT_K$.

We use $\rightharpoonup$ to denote weak convergence in the sense of analysts;
that is, $u^\epsilon\rightharpoonup u$ in $L^1$ means $\int u^\epsilon v \dif x
\rightarrow\int uv\dif x$ for all $v\in L^\infty$.

We write $L_t^2(H^1)$ for functions for which the $H^1$ norm in
space is in $L^2$ with respect to time, i.e.
$$\int_0^T\int \left\{u(t,x)^2+\left(\frac{d}{dx} u(t,x)\right)^2\right\} \dif x \dif t <\infty,$$
and $C_t(L^1)$
will denote functions for which the $L^1$ norm in space is continuous in time.
\end{notation}

\begin{proposition}
Suppose that $u_0^\epsilon\in L^1(\IT_K)$, $u_0^\epsilon\geq 0$, and
$\sup_\epsilon\int u_0^\epsilon|\log u_0^\epsilon|dx<\infty$ with
$u_0^\epsilon\rightharpoonup u_0^\epsilon$ as $\epsilon\to 0$. Then
writing $u^\epsilon$ for the solution to~(\ref{mollified equation})
on $[0,T]\times \IT_K$ with
initial condition $u_0^\epsilon$,
$u^\epsilon\rightharpoonup u$ as $\epsilon\to 0$ where
$u\in L_t^2(H^1)\cap C_t(L^1)$, $\int u|\log u| dx<\infty$, and
$u$ solves~(\ref{PME}) on $[0,T]\times \IT_K$. Moreover, strong convergence
of the initial conditions implies strong convergence of the solutions.
\end{proposition}
%\noindent
%{\bf Proof}
\begin{proof}

Our proof owes a lot to~\cite{lions/mas-gallic:2001}.
First observe that
\begin{multline*}
\int u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\dif x
= \int\int\int u^\epsilon(x)u^\epsilon(x-y)\rho_\epsilon(y-z)
\check{\rho}_\epsilon(z)\dif z\dif y\dif x
\\
=
\int\int\int u^\epsilon(\tilde{x}-\tilde{z})
u^\epsilon(\tilde{x}-\tilde{y})
\rho_\epsilon(\tilde{y})
\rho_\epsilon(\tilde{z})\dif \tilde{z}\dif \tilde{y}\dif \tilde{x}
=\int\left(u^\epsilon*\rho_\epsilon\right(x))^2\dif x,
\end{multline*}
where we have set $\tilde{x}=x-z$, $\tilde{y}=y-z$, $\tilde{z}=-z$.

Now note that
$$\frac{d}{dt}\int u^\epsilon (t,x) \dif x=\int \Delta (u^\epsilon*\zeta_\epsilon)\dif x
+\int u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\dif x= \int u^\epsilon \dif x
-\int (u^\epsilon*\rho)^2 \dif x.$$
Thus $\int u^\epsilon(t,x)\dif x$ is uniformly bounded above in $t$
and $\epsilon$ on $[0,T]$. Note that this also then gives a uniform
bound on the rate of change of $\int u^\epsilon (t,x) \dif x$, and since
we are working on $[0,T]$ this will be enough to give continuity in time of the
$L^1$ norm of the limit
when we pass to a convergent subsequence.

Now consider
\begin{eqnarray*}
\frac{d}{dt}\int u^\epsilon\log u^\epsilon \dif x &=&
\int (1+\log u^\epsilon)\left[\Delta (u^\epsilon\cdot
u^\epsilon*\zeta_\epsilon)+u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right]
\dif x
\\
&=&
\int (1+\log u^\epsilon)\left[\nabla\left(u^\epsilon\cdot
\nabla(u^\epsilon*\zeta_\epsilon)+
\nabla u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right)
+u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right] \dif x
\\
&=&
\int \left[-\frac{\nabla u^\epsilon}{u^\epsilon}
\left(u^\epsilon\cdot \nabla(u^\epsilon*\zeta_\epsilon)
+\nabla u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right)+
(1+\log u^\epsilon)u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right]\dif x
\\
&=&
-\int \left(\nabla (u^\epsilon*\rho_\epsilon)\right)^2 \dif x
-\int (\nabla u^\epsilon)^2\frac{u^\epsilon*\zeta_\epsilon}{u^\epsilon} \dif x
\\
&&+\int
\left[u^\epsilon+u^\epsilon\log u^\epsilon(1-u^\epsilon*\zeta_\epsilon)
-u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right]\dif x\\
&=&
-\int \left(\nabla (u^\epsilon*\rho_\epsilon)\right)^2 \dif x
-\int (\nabla u^\epsilon)^2\frac{u^\epsilon*\zeta_\epsilon}{u^\epsilon} \dif x
-\int (u^\epsilon*\rho_\epsilon)^2\dif x
\\
&&+\int
\left[u^\epsilon+u^\epsilon\log u^\epsilon(1-u^\epsilon*\zeta_\epsilon)
%-u^\epsilon\cdot u^\epsilon*\zeta_\epsilon
\right]\dif x .
\end{eqnarray*}
The first three terms are negative; and we already
saw that the $L^1$ norm
of $u^\epsilon$ is uniformly bounded.
Moreover, since $u^\epsilon\log u^\epsilon$ is uniformly bounded below,
$$-\int u^\epsilon \log u^\epsilon \cdot u^\epsilon*\zeta_\epsilon \dif x
\leq C\int u^\epsilon*\zeta_\epsilon \dif x=\int u^\epsilon \dif x.$$
From this we see immediately that $\int u^\epsilon \log u^\epsilon \dif x$
is uniformly bounded
above in $\epsilon$ and $t\in [0,T]$. Moreover,
since we are working on the bounded space $\IT_K$, the lower bound
on $u^\epsilon\log u^\epsilon$ also allows us to
bound $\int u^\epsilon\log u^\epsilon \dif x$ uniformly
below, from which we deduce that
we have a uniform bound on $\int u^\epsilon|\log u^\epsilon| \dif x$.
This in turn means that both
$\int_0^t (u^\epsilon*\rho_\epsilon)^2 \dif x$ and
$\int_0^t \big(\nabla (u^\epsilon*\rho_\epsilon)\big)^2 \dif x$
are uniformly bounded in
$\epsilon$ and $t\in [0,T]$.
Now observe that
\begin{equation}
\label{total equation}
\int\Delta\left((u^\epsilon*\zeta_\epsilon)u^\epsilon\right)\phi \dif x =
\int \nabla(u^\epsilon*\zeta_\epsilon)\cdot
u^\epsilon\cdot\nabla\phi \dif x +\int u^\epsilon*\zeta_\epsilon
\cdot\nabla u^\epsilon
\cdot \nabla\phi \dif x.
\end{equation}
For the first term
\begin{eqnarray}
\nonumber
\int \nabla(u^\epsilon*\zeta_\epsilon)\cdot u^\epsilon\cdot\nabla\phi \dif x
&=&
\int\int\int\nabla u^\epsilon(x-y)\rho_\epsilon(y-z)\check{\rho}_\epsilon(z)
u^\epsilon(x)\nabla\phi(x)\dif z \dif y \dif x
\\
\nonumber
&=&
\int\int\int\nabla u^\epsilon(\tilde{x}-\tilde{y})\rho_\epsilon(\tilde{y})
\rho_\epsilon(\tilde{z})u^\epsilon(\tilde{x}-\tilde{z})
\nabla\phi(\tilde{x}-\tilde{z})\dif \tilde{z}\dif \tilde{y} \dif \tilde{x}
\\
\nonumber
&=&\int(\nabla u^\epsilon*\rho_\epsilon)\cdot
\left((u^\epsilon\nabla\phi)*\rho_\epsilon\right)
\dif x\\
\nonumber
&=&
\frac{1}{2}\int\nabla ((u^\epsilon*\rho_\epsilon)^2)\cdot\nabla\phi \dif x
\\
\label{error 1}
&&+
\int\nabla(u^\epsilon*\rho_\epsilon)
\left[(u^\epsilon\cdot\nabla\phi)*\rho_\epsilon-
\nabla\phi\cdot((u^\epsilon*\rho_\epsilon)\right]\dif x,
\end{eqnarray}
where, as before, we have substituted $\tilde{x}=x-z$, $\tilde{y}=y-z$,
$\tilde{z}=-z$.
